---
title: "P8105_HW5_TEM2171"
author: "Teresa Moore"
date: "2023-11-15"
output: html_document
---
```{r load_libraries}
library(tidyverse)
```

# PROBLEM 2

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

```{r setup, include=FALSE}
all_participants_df <- 
  tibble(
    files = list.files("data"),
    path = str_c("data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()

all_participants_tidy_df <- 
  all_participants_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)
  ) %>% 
  pivot_longer(
    cols = starts_with("week_"),
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_"
  ) %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups:

```{r}
all_participants_tidy_df |> 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + geom_path() + facet_grid(~group)
```

For the control arm, the outcomes on average stay the same while for the experimental arm, we see on average an increaase in the outcomes.

#PROBLEM 3
First set the following design elements:

```{r}
n <- 30
sigma <- 5
alpha <- 0.05
num_simulations <- 5000
```

```{r}
t_test_simulation = function(mu) {
  
  simulation_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma)
  )
  
  test = t.test(x ~ 1, data = simulation_data)
  
  broom::tidy(test) 
  
}
```

```{r}
simulation_test_results <- 
  tibble(mu = 0:6) %>% 
  mutate(
    output_lists = map(mu, ~rerun(num_simulations, t_test_simulation(.x))),
    estimate_dfs = map(output_lists, bind_rows)
  ) %>% 
  select(-output_lists)

simulation_test_results = 
  simulation_test_results %>% 
  unnest(estimate_dfs) %>% 
  select(mu, estimate, p.value) %>% 
  mutate(significant = as.numeric(p.value < alpha))

```

```{r}
summary_all = 
  simulation_test_results %>% 
  group_by(mu) %>%
  summarize(average = mean(estimate)) %>% 
  mutate(case = "all")

summary_signif = 
  simulation_test_results %>% 
  filter(p.value < alpha) %>% 
  group_by(mu) %>%
  summarize(average = mean(estimate)) %>% 
  mutate(case = "signif only")

bind_rows(summary_all, summary_signif) %>% 
  ggplot(aes(x = mu, y = average, color = case)) + 
  geom_point() +
  geom_path() 
```

```{r}
simulation_test_results %>% 
  ggplot(aes(x = estimate)) + geom_histogram() + 
  facet_grid(significant ~ mu)
```
